Effects of CHILDREN's programs

### 2020-02-27 paper.Rnw

\begin{abstract} 
abstract on separate page
100 - 150 words
\end{abstract}

>>>>

\begin{abstract} 
This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'. We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables. We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus. Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
\end{abstract}
